MLB Team Statistics between 2000 - 2023 on Predicting Games Won per Season ^[Code and data are available at: https://github.com/YcartXin/MLB_Team_Stats]

### 2024-04-05 paper/paper.qmd
Updated paper and simulated data

---
title: "MLB Team Statistics between 2000 - 2023 on Predicting Games Won per Season ^[Code and data are available at: https://github.com/YcartXin/MLB_Team_Stats]"
author: 
  - Tracy Yang
date: today
date-format: long
abstract: "Using MLB key team statistics between 2000 and 2023, this paper investigates the outcome of the 2024 season using each team's current statistics on predicting their total wins out of 162 games. We also investigate the common conception that baseball is a numbers game by evaluating the predictability of wins that a team would obtain during a seasion from looking at their batting average (AVG), defensive efficiency ratio (DER), and earned run average (ERA)."
format: 
  typst:
    toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

Important statistics for a team in this paper is defined as the team's batting average (AVG), defensive efficiency ratio (DER), and earned run average (ERA). These three statistics each refer to an important aspect of a strong team: hitting, pitching, and fielding prospectively. The specifics of these indicators will be elaborated on in @sec-data. Many 2024 season predictions exist...

@@

# Model

@@

## Second discussion point

## Third discussion point

>>>>

---
title: "MLB Team Statistics between 2000 - 2023 on Predicting Games Won per Season ^[Code and data are available at: https://github.com/YcartXin/MLB_Team_Stats]"
author: 
  - Tracy Yang
date: today
date-format: long
abstract: "Using MLB key team statistics between 2000 and 2023, this paper investigates the outcome of the 2024 season using each team's current statistics on predicting their total wins out of 162 games. We also investigate the common conception that baseball is a numbers game by evaluating the predictability of wins that a team would obtain during a seasion from looking at their batting average (AVG), defensive efficiency ratio (DffEff), and earned run average (ERA)."
format: 
  typst:
    toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

Important statistics for a team in this paper is defined as the team's batting average (AVG), defensive efficiency ratio (DffEff), and earned run average (ERA). These three statistics each refer to an important aspect of a strong team: hitting, pitching, and fielding prospectively. The specifics of these indicators will be elaborated on in @sec-data. Among present research, 2024 season predictions exist, however, they mainly focus on the win for a game or series for betting purposes. This paper is unique in its approach to predict and investigates the predictability of overall seasonal wins for baseball teams.

The rest of the paper is structured as follows. @sec-data (Data) will explain the source of the data used, its collection process, and the process of cleaning that led to the final data used as well as potential biases. @sec-model...

The overall analysis shows...

@@

# Model {#sec-model}

@@
